A thesis draft

### 2018-11-24 res/sections/08-Background.tex

In this chapter we are going to explain the most important concepts of the 
upcoming 5G standard, talking about the Virtual Network Functions (VNFs) and 
how first experiments with this new technology already begun. Finally we are 
going to briefly introduce and explain the technologies involved and their role.

>>>>

In this chapter we are going to explain the most important concepts of the
upcoming 5G standard, talking about the Virtual Network Functions (VNFs), the
Network Slice (NS) concept and how first experiments with these new innovations
already begun. Finally we are going to briefly introduce and explain the
technologies involved and their role.
